Modelling the gas kinematics of an atypical Lyman alpha emitting compact dwarf galaxy

### 2017-09-01 paper/paper.tex
new references updated disucssion

The models we use correspond to simplified geometrical configurations.
This allows us to perform a deep exploration of parameter space and
gain some physical insight into \tol's kinematic properties.
In this paper we show, for the first time in the literature, that \tol's
\lya profile can be explicitly modeled by either of these two
models. 
The hybrid case of a rotating multiphase configuration is also of
interest, but cannot be simulated with in current models. 
However, it is the subject of ongoing work  (Remolina-Gutierrez et
al. in prep.).

@@

Which model has more
chances to be correct?  
We argue that that the rotation model should be discarded by
considering that the prefered rotational velocity of $V_{m}\sim350$
\kms\ is of the same order as the largest rotational velocity of giant
disc galaxies that have two orders of magnitude more baryonic mass
than \tol\ \citep{2015MNRAS.448.1767C}.

@@

\bibliographystyle{mnras}
%\bibliography{references}
\begin{thebibliography}{}
\makeatletter
\relax
\def\mn@urlcharsother{\let\do\@makeother \do\$\do\&\do\#\do\^\do\_\do\%\do\~}
\def\mn@doi{\begingroup\mn@urlcharsother \@ifnextchar [ {\mn@doi@}
  {\mn@doi@[]}}
\def\mn@doi@[#1]#2{\def\@tempa{#1}\ifx\@tempa\@empty \href
  {http://dx.doi.org/#2} {doi:#2}\else \href {http://dx.doi.org/#2} {#1}\fi
  \endgroup}
\def\mn@eprint#1#2{\mn@eprint@#1:#2::\@nil}
\def\mn@eprint@arXiv#1{\href {http://arxiv.org/abs/#1} {{\tt arXiv:#1}}}
\def\mn@eprint@dblp#1{\href {http://dblp.uni-trier.de/rec/bibtex/#1.xml}
  {dblp:#1}}
\def\mn@eprint@#1:#2:#3:#4\@nil{\def\@tempa {#1}\def\@tempb {#2}\def\@tempc
  {#3}\ifx \@tempc \@empty \let \@tempc \@tempb \let \@tempb \@tempa \fi \ifx
  \@tempb \@empty \def\@tempb {arXiv}\fi \@ifundefined
  {mn@eprint@\@tempb}{\@tempb:\@tempc}{\expandafter \expandafter \csname
  mn@eprint@\@tempb\endcsname \expandafter{\@tempc}}}

\bibitem[\protect\citeauthoryear{{Astropy Collaboration} et~al.,}{{Astropy
  Collaboration} et~al.}{2013}]{astropy}
{Astropy Collaboration} et~al., 2013, \mn@doi [\aap]
  {10.1051/0004-6361/201322068}, \href
  {http://adsabs.harvard.edu/abs/2013A%26A...558A..33A} {558, A33}

\bibitem[\protect\citeauthoryear{{Bacon} et~al.,}{{Bacon}
  et~al.}{2014}]{2014Msngr.157...13B}
{Bacon} R.,  et~al., 2014, The Messenger, \href
  {http://adsabs.harvard.edu/abs/2014Msngr.157...13B} {157, 13}

\bibitem[\protect\citeauthoryear{{Begum}, {Chengalur}  \&
  {Karachentsev}}{{Begum} et~al.}{2005}]{2005A&A...433L...1B}
{Begum} A.,  {Chengalur} J.~N.,   {Karachentsev} I.~D.,  2005, \mn@doi [\aap]
  {10.1051/0004-6361:200500026}, \href
  {http://adsabs.harvard.edu/abs/2005A%26A...433L...1B} {433, L1}

\bibitem[\protect\citeauthoryear{{Courtois}, {Zaritsky}, {Sorce}  \&
  {Pomar{\`e}de}}{{Courtois} et~al.}{2015}]{2015MNRAS.448.1767C}
{Courtois} H.~M.,  {Zaritsky} D.,  {Sorce} J.~G.,   {Pomar{\`e}de} D.,  2015,
  \mn@doi [\mnras] {10.1093/mnras/stv071}, \href
  {http://adsabs.harvard.edu/abs/2015MNRAS.448.1767C} {448, 1767}

\bibitem[\protect\citeauthoryear{{Dey}, {Spinrad}, {Stern}, {Graham}  \&
  {Chaffee}}{{Dey} et~al.}{1998}]{1998ApJ...498L..93D}
{Dey} A.,  {Spinrad} H.,  {Stern} D.,  {Graham} J.~R.,   {Chaffee} F.~H.,
  1998, \mn@doi [\apjl] {10.1086/311331}, \href
  {http://adsabs.harvard.edu/abs/1998ApJ...498L..93D} {498, L93}

\bibitem[\protect\citeauthoryear{{Dijkstra}}{{Dijkstra}}{2014}]{2014PASA...31...40D}
{Dijkstra} M.,  2014, \mn@doi [\pasa] {10.1017/pasa.2014.33}, \href
  {http://adsabs.harvard.edu/abs/2014PASA...31...40D} {31, e040}

\bibitem[\protect\citeauthoryear{{Dijkstra} \& {Kramer}}{{Dijkstra} \&
  {Kramer}}{2012}]{2012MNRAS.424.1672D}
{Dijkstra} M.,  {Kramer} R.,  2012, \mn@doi [\mnras]
  {10.1111/j.1365-2966.2012.21131.x}, \href
  {http://adsabs.harvard.edu/abs/2012MNRAS.424.1672D} {424, 1672}

\bibitem[\protect\citeauthoryear{{Dijkstra}, {Lidz}  \& {Wyithe}}{{Dijkstra}
  et~al.}{2007}]{2007MNRAS.377.1175D}
{Dijkstra} M.,  {Lidz} A.,   {Wyithe} J.~S.~B.,  2007, \mn@doi [\mnras]
  {10.1111/j.1365-2966.2007.11666.x}, \href
  {http://adsabs.harvard.edu/abs/2007MNRAS.377.1175D} {377, 1175}

\bibitem[\protect\citeauthoryear{{Engelbracht}, {Rieke}, {Gordon}, {Smith},
  {Werner}, {Moustakas}, {Willmer}  \& {Vanzi}}{{Engelbracht}
  et~al.}{2008}]{2008ApJ...678..804E}
{Engelbracht} C.~W.,  {Rieke} G.~H.,  {Gordon} K.~D.,  {Smith} J.-D.~T.,
  {Werner} M.~W.,  {Moustakas} J.,  {Willmer} C.~N.~A.,   {Vanzi} L.,  2008,
  \mn@doi [\apj] {10.1086/529513}, \href
  {http://adsabs.harvard.edu/abs/2008ApJ...678..804E} {678, 804}

\bibitem[\protect\citeauthoryear{{Erb} et~al.,}{{Erb} et~al.}{2014}]{Erb14}
{Erb} D.~K.,  et~al., 2014, \mn@doi [\apj] {10.1088/0004-637X/795/1/33}, \href
  {http://adsabs.harvard.edu/abs/2014ApJ...795...33E} {795, 33}

\bibitem[\protect\citeauthoryear{{Eskew}, {Zaritsky}  \& {Meidt}}{{Eskew}
  et~al.}{2012}]{2012AJ....143..139E}
{Eskew} M.,  {Zaritsky} D.,   {Meidt} S.,  2012, \mn@doi [\aj]
  {10.1088/0004-6256/143/6/139}, \href
  {http://adsabs.harvard.edu/abs/2012AJ....143..139E} {143, 139}

\bibitem[\protect\citeauthoryear{{Foreman-Mackey}, {Hogg}, {Lang}  \&
  {Goodman}}{{Foreman-Mackey} et~al.}{2013}]{2013PASP..125..306F}
{Foreman-Mackey} D.,  {Hogg} D.~W.,  {Lang} D.,   {Goodman} J.,  2013, \mn@doi
  [\pasp] {10.1086/670067}, \href
  {http://adsabs.harvard.edu/abs/2013PASP..125..306F} {125, 306}

\bibitem[\protect\citeauthoryear{{Forero-Romero}, {Yepes}, {Gottl{\"o}ber},
  {Knollmann}, {Cuesta}  \& {Prada}}{{Forero-Romero} et~al.}{2011}]{CLARA}
{Forero-Romero} J.~E.,  {Yepes} G.,  {Gottl{\"o}ber} S.,  {Knollmann} S.~R.,
  {Cuesta} A.~J.,   {Prada} F.,  2011, \mn@doi [\mnras]
  {10.1111/j.1365-2966.2011.18983.x}, \href
  {http://adsabs.harvard.edu/abs/2011MNRAS.415.3666F} {415, 3666}

\bibitem[\protect\citeauthoryear{{Fricke}, {Izotov}, {Papaderos}, {Guseva}  \&
  {Thuan}}{{Fricke} et~al.}{2001}]{2001AJ....121..169F}
{Fricke} K.~J.,  {Izotov} Y.~I.,  {Papaderos} P.,  {Guseva} N.~G.,   {Thuan}
  T.~X.,  2001, \mn@doi [\aj] {10.1086/318016}, \href
  {http://adsabs.harvard.edu/abs/2001AJ....121..169F} {121, 169}

\bibitem[\protect\citeauthoryear{{Garavito-Camargo}, {Forero-Romero}  \&
  {Dijkstra}}{{Garavito-Camargo} et~al.}{2014}]{GaravitoCamargo2014}
{Garavito-Camargo} J.~N.,  {Forero-Romero} J.~E.,   {Dijkstra} M.,  2014,
  \mn@doi [\apj] {10.1088/0004-637X/795/2/120}, \href
  {http://adsabs.harvard.edu/abs/2014ApJ...795..120G} {795, 120}

\bibitem[\protect\citeauthoryear{{Gavil{\'a}n}, {Ascasibar}, {Moll{\'a}}  \&
  {D{\'{\i}}az}}{{Gavil{\'a}n} et~al.}{2013}]{2013MNRAS.434.2491G}
{Gavil{\'a}n} M.,  {Ascasibar} Y.,  {Moll{\'a}} M.,   {D{\'{\i}}az} {\'A}.~I.,
  2013, \mn@doi [\mnras] {10.1093/mnras/stt1186}, \href
  {http://adsabs.harvard.edu/abs/2013MNRAS.434.2491G} {434, 2491}

\bibitem[\protect\citeauthoryear{{Gawiser} et~al.,}{{Gawiser}
  et~al.}{2007}]{2007ApJ...671..278G}
{Gawiser} E.,  et~al., 2007, \mn@doi [\apj] {10.1086/522955}, \href
  {http://adsabs.harvard.edu/abs/2007ApJ...671..278G} {671, 278}

\bibitem[\protect\citeauthoryear{{Geha}, {Guhathakurta}  \& {van der
  Marel}}{{Geha} et~al.}{2003}]{2003AJ....126.1794G}
{Geha} M.,  {Guhathakurta} P.,   {van der Marel} R.~P.,  2003, \mn@doi [\aj]
  {10.1086/377624}, \href {http://adsabs.harvard.edu/abs/2003AJ....126.1794G}
  {126, 1794}

\bibitem[\protect\citeauthoryear{Goodman \& Weare}{Goodman \&
  Weare}{2010}]{goodman2010ensemble}
Goodman J.,  Weare J.,  2010, Communications in applied mathematics and
  computational science, 5, 65

\bibitem[\protect\citeauthoryear{{Greig}, {Komatsu}  \& {Wyithe}}{{Greig}
  et~al.}{2013}]{2013MNRAS.431.1777G}
{Greig} B.,  {Komatsu} E.,   {Wyithe} J.~S.~B.,  2013, \mn@doi [\mnras]
  {10.1093/mnras/stt292}, \href
  {http://adsabs.harvard.edu/abs/2013MNRAS.431.1777G} {431, 1777}

\bibitem[\protect\citeauthoryear{{Gronke} \& {Dijkstra}}{{Gronke} \&
  {Dijkstra}}{2016}]{Gronke2016}
{Gronke} M.,  {Dijkstra} M.,  2016, \mn@doi [\apj]
  {10.3847/0004-637X/826/1/14}, \href
  {http://adsabs.harvard.edu/abs/2016ApJ...826...14G} {826, 14}

\bibitem[\protect\citeauthoryear{{Gronke}, {Bull}  \& {Dijkstra}}{{Gronke}
  et~al.}{2015}]{2015ApJ...812..123G}
{Gronke} M.,  {Bull} P.,   {Dijkstra} M.,  2015, \mn@doi [\apj]
  {10.1088/0004-637X/812/2/123}, \href
  {http://adsabs.harvard.edu/abs/2015ApJ...812..123G} {812, 123}

\bibitem[\protect\citeauthoryear{{Harrington}}{{Harrington}}{1973}]{Harrington73}
{Harrington} J.~P.,  1973, \mnras, \href
  {http://adsabs.harvard.edu/abs/1973MNRAS.162...43H} {162, 43}

\bibitem[\protect\citeauthoryear{{Hayashino} et~al.,}{{Hayashino}
  et~al.}{2004}]{2004AJ....128.2073H}
{Hayashino} T.,  et~al., 2004, \mn@doi [\aj] {10.1086/424935}, \href
  {http://adsabs.harvard.edu/abs/2004AJ....128.2073H} {128, 2073}

\bibitem[\protect\citeauthoryear{{Hayes}}{{Hayes}}{2015}]{Hayes15}
{Hayes} M.,  2015, \mn@doi [\pasa] {10.1017/pasa.2015.25}, \href
  {http://adsabs.harvard.edu/abs/2015PASA...32...27H} {32, e027}

\bibitem[\protect\citeauthoryear{{Herenz} et~al.,}{{Herenz}
  et~al.}{2016}]{Herenz16}
{Herenz} E.~C.,  et~al., 2016, \mn@doi [\aap] {10.1051/0004-6361/201527373},
  \href {http://adsabs.harvard.edu/abs/2016A%26A...587A..78H} {587, A78}

\bibitem[\protect\citeauthoryear{{Hummer} \& {Storey}}{{Hummer} \&
  {Storey}}{1987}]{Hummer1987}
{Hummer} D.~G.,  {Storey} P.~J.,  1987, \mn@doi [\mnras]
  {10.1093/mnras/224.3.801}, \href
  {http://adsabs.harvard.edu/abs/1987MNRAS.224..801H} {224, 801}

\bibitem[\protect\citeauthoryear{{Hunter}}{{Hunter}}{2007}]{matplotlib}
{Hunter} J.~D.,  2007, \mn@doi [Computing in Science and Engineering]
  {10.1109/MCSE.2007.55}, \href
  {http://adsabs.harvard.edu/abs/2007CSE.....9...90H} {9, 90}

\bibitem[\protect\citeauthoryear{{Izotov}, {Papaderos}, {Guseva}, {Fricke}  \&
  {Thuan}}{{Izotov} et~al.}{2004}]{Izotov04}
{Izotov} Y.~I.,  {Papaderos} P.,  {Guseva} N.~G.,  {Fricke} K.~J.,   {Thuan}
  T.~X.,  2004, \mn@doi [\aap] {10.1051/0004-6361:20035847}, \href
  {http://adsabs.harvard.edu/abs/2004A%26A...421..539I} {421, 539}

\bibitem[\protect\citeauthoryear{James, Witten  \& Hastie}{James
  et~al.}{2014}]{james2014introduction}
James G.,  Witten D.,   Hastie T.,  2014, An Introduction to Statistical
  Learning: With Applications in R.

\bibitem[\protect\citeauthoryear{{Kennicutt}}{{Kennicutt}}{1998}]{Kennicutt98}
{Kennicutt} Jr. R.~C.,  1998, \mn@doi [\araa] {10.1146/annurev.astro.36.1.189},
  \href {http://adsabs.harvard.edu/abs/1998ARA%26A..36..189K} {36, 189}

\bibitem[\protect\citeauthoryear{Kluyver et~al.,}{Kluyver
  et~al.}{2016}]{jupyter}
Kluyver T.,  et~al., 2016, in ELPUB. pp 87--90

\bibitem[\protect\citeauthoryear{{Kova{\v c}}, {Somerville}, {Rhoads},
  {Malhotra}  \& {Wang}}{{Kova{\v c}} et~al.}{2007}]{2007ApJ...668...15K}
{Kova{\v c}} K.,  {Somerville} R.~S.,  {Rhoads} J.~E.,  {Malhotra} S.,   {Wang}
  J.,  2007, \mn@doi [\apj] {10.1086/520668}, \href
  {http://adsabs.harvard.edu/abs/2007ApJ...668...15K} {668, 15}

\bibitem[\protect\citeauthoryear{{Laursen}, {Duval}  \& {{\"O}stlin}}{{Laursen}
  et~al.}{2013}]{Laursen2013ApJ...766..124L}
{Laursen} P.,  {Duval} F.,   {{\"O}stlin} G.,  2013, \mn@doi [\apj]
  {10.1088/0004-637X/766/2/124}, \href
  {http://adsabs.harvard.edu/abs/2013ApJ...766..124L} {766, 124}

\bibitem[\protect\citeauthoryear{{Loeb} \& {Rybicki}}{{Loeb} \&
  {Rybicki}}{1999}]{LoebRybicki}
{Loeb} A.,  {Rybicki} G.~B.,  1999, \mn@doi [\apj] {10.1086/307844}, \href
  {http://adsabs.harvard.edu/abs/1999ApJ...524..527L} {524, 527}

\bibitem[\protect\citeauthoryear{{Martin}}{{Martin}}{1998}]{1998ApJ...506..222M}
{Martin} C.~L.,  1998, \mn@doi [\apj] {10.1086/306219}, \href
  {http://adsabs.harvard.edu/abs/1998ApJ...506..222M} {506, 222}

\bibitem[\protect\citeauthoryear{{Mas-Hesse}, {Kunth}, {Tenorio-Tagle},
  {Leitherer}, {Terlevich}  \& {Terlevich}}{{Mas-Hesse}
  et~al.}{2003}]{mashesse03}
{Mas-Hesse} J.~M.,  {Kunth} D.,  {Tenorio-Tagle} G.,  {Leitherer} C.,
  {Terlevich} R.~J.,   {Terlevich} E.,  2003, \mn@doi [\apj] {10.1086/379116},
  \href {http://adsabs.harvard.edu/abs/2003ApJ...598..858M} {598, 858}

\bibitem[\protect\citeauthoryear{{McCourt}, {Oh}, {O'Leary}  \&
  {Madigan}}{{McCourt} et~al.}{2016}]{2016arXiv161001164M}
{McCourt} M.,  {Oh} S.~P.,  {O'Leary} R.~M.,   {Madigan} A.-M.,  2016,
  preprint, \href {http://esoads.eso.org/abs/2016arXiv161001164M} {}
  (\mn@eprint {arXiv} {1610.01164})

\bibitem[\protect\citeauthoryear{{McKee} \& {Ostriker}}{{McKee} \&
  {Ostriker}}{1977}]{1977ApJ...218..148M}
{McKee} C.~F.,  {Ostriker} J.~P.,  1977, \mn@doi [\apj] {10.1086/155667}, \href
  {http://esoads.eso.org/abs/1977ApJ...218..148M} {218, 148}

\bibitem[\protect\citeauthoryear{McKinney et~al.}{McKinney
  et~al.}{2010}]{pandas}
McKinney W.,  et~al., 2010, in Proceedings of the 9th Python in Science
  Conference. pp 51--56

\bibitem[\protect\citeauthoryear{{Mej{\'{\i}}a-Restrepo} \&
  {Forero-Romero}}{{Mej{\'{\i}}a-Restrepo} \&
  {Forero-Romero}}{2016}]{2016ApJ...828....5M}
{Mej{\'{\i}}a-Restrepo} J.~E.,  {Forero-Romero} J.~E.,  2016, \mn@doi [\apj]
  {10.3847/0004-637X/828/1/5}, \href
  {http://adsabs.harvard.edu/abs/2016ApJ...828....5M} {828, 5}

\bibitem[\protect\citeauthoryear{{Neufeld}}{{Neufeld}}{1991}]{1991ApJ...370L..85N}
{Neufeld} D.~A.,  1991, \mn@doi [\apjl] {10.1086/185983}, \href
  {http://adsabs.harvard.edu/abs/1991ApJ...370L..85N} {370, L85}

\bibitem[\protect\citeauthoryear{{Noeske}, {Papaderos}, {Cair{\'o}s}  \&
  {Fricke}}{{Noeske} et~al.}{2003}]{2003A&A...410..481N}
{Noeske} K.~G.,  {Papaderos} P.,  {Cair{\'o}s} L.~M.,   {Fricke} K.~J.,  2003,
  \mn@doi [\aap] {10.1051/0004-6361:20031147}, \href
  {http://adsabs.harvard.edu/abs/2003A%26A...410..481N} {410, 481}

\bibitem[\protect\citeauthoryear{{Orsi}, {Lacey}, {Baugh}  \& {Infante}}{{Orsi}
  et~al.}{2008}]{2008MNRAS.391.1589O}
{Orsi} A.,  {Lacey} C.~G.,  {Baugh} C.~M.,   {Infante} L.,  2008, \mn@doi
  [\mnras] {10.1111/j.1365-2966.2008.14010.x}, \href
  {http://adsabs.harvard.edu/abs/2008MNRAS.391.1589O} {391, 1589}

\bibitem[\protect\citeauthoryear{{Orsi}, {Lacey}  \& {Baugh}}{{Orsi}
  et~al.}{2012}]{Orsi12}
{Orsi} A.,  {Lacey} C.~G.,   {Baugh} C.~M.,  2012, \mn@doi [\mnras]
  {10.1111/j.1365-2966.2012.21396.x}, \href
  {http://adsabs.harvard.edu/abs/2012MNRAS.425...87O} {425, 87}

\bibitem[\protect\citeauthoryear{{{\"O}stlin} et~al.,}{{{\"O}stlin}
  et~al.}{2014}]{LARS}
{{\"O}stlin} G.,  et~al., 2014, \mn@doi [\apj] {10.1088/0004-637X/797/1/11},
  \href {http://adsabs.harvard.edu/abs/2014ApJ...797...11O} {797, 11}

\bibitem[\protect\citeauthoryear{{Ott}, {Walter}  \& {Brinks}}{{Ott}
  et~al.}{2005}]{2005MNRAS.358.1453O}
{Ott} J.,  {Walter} F.,   {Brinks} E.,  2005, \mn@doi [\mnras]
  {10.1111/j.1365-2966.2005.08863.x}, \href
  {http://adsabs.harvard.edu/abs/2005MNRAS.358.1453O} {358, 1453}

\bibitem[\protect\citeauthoryear{{Padilla}, {Christlein}, {Gawiser},
  {Gonz{\'a}lez}, {Guaita}  \& {Infante}}{{Padilla}
  et~al.}{2010}]{2010MNRAS.409..184P}
{Padilla} N.~D.,  {Christlein} D.,  {Gawiser} E.,  {Gonz{\'a}lez} R.~E.,
  {Guaita} L.,   {Infante} L.,  2010, \mn@doi [\mnras]
  {10.1111/j.1365-2966.2010.17317.x}, \href
  {http://adsabs.harvard.edu/abs/2010MNRAS.409..184P} {409, 184}

\bibitem[\protect\citeauthoryear{{Partridge} \& {Peebles}}{{Partridge} \&
  {Peebles}}{1967}]{PartridgePeebles}
{Partridge} R.~B.,  {Peebles} P.~J.~E.,  1967, \mn@doi [\apj] {10.1086/149079},
  \href {http://adsabs.harvard.edu/abs/1967ApJ...147..868P} {147, 868}

\bibitem[\protect\citeauthoryear{Pedregosa et~al.,}{Pedregosa
  et~al.}{2011}]{scikit-learn}
Pedregosa F.,  et~al., 2011, Journal of Machine Learning Research, 12, 2825

\bibitem[\protect\citeauthoryear{P\'erez \& Granger}{P\'erez \&
  Granger}{2007}]{IPython}
P\'erez F.,  Granger B.~E.,  2007, \mn@doi [Computing in Science and
  Engineering] {10.1109/MCSE.2007.53}, 9, 21

\bibitem[\protect\citeauthoryear{{Poveda-Ruiz}, {Forero-Romero}  \&
  {Mu{\~n}oz-Cuartas}}{{Poveda-Ruiz} et~al.}{2016}]{2016ApJ...832..169P}
{Poveda-Ruiz} C.~N.,  {Forero-Romero} J.~E.,   {Mu{\~n}oz-Cuartas} J.~C.,
  2016, \mn@doi [\apj] {10.3847/0004-637X/832/2/169}, \href
  {http://adsabs.harvard.edu/abs/2016ApJ...832..169P} {832, 169}

\bibitem[\protect\citeauthoryear{{Prada}, {Klypin}, {Cuesta}, {Betancort-Rijo}
  \& {Primack}}{{Prada} et~al.}{2012}]{2012MNRAS.423.3018P}
{Prada} F.,  {Klypin} A.~A.,  {Cuesta} A.~J.,  {Betancort-Rijo} J.~E.,
  {Primack} J.,  2012, \mn@doi [\mnras] {10.1111/j.1365-2966.2012.21007.x},
  \href {http://adsabs.harvard.edu/abs/2012MNRAS.423.3018P} {423, 3018}

\bibitem[\protect\citeauthoryear{{Pustilnik} \& {Martin}}{{Pustilnik} \&
  {Martin}}{2007}]{pustilnikmartin07}
{Pustilnik} S.~A.,  {Martin} J.-M.,  2007, \mn@doi [\aap]
  {10.1051/0004-6361:20066137}, \href
  {http://cdsads.u-strasbg.fr/abs/2007A%26A...464..859P} {464, 859}

\bibitem[\protect\citeauthoryear{{Rivera-Thorsen} et~al.,}{{Rivera-Thorsen}
  et~al.}{2015}]{2015ApJ...805...14R}
{Rivera-Thorsen} T.~E.,  et~al., 2015, \mn@doi [\apj]
  {10.1088/0004-637X/805/1/14}, \href
  {http://adsabs.harvard.edu/abs/2015ApJ...805...14R} {805, 14}

\bibitem[\protect\citeauthoryear{{Roth} et~al.,}{{Roth} et~al.}{2005}]{PMAS}
{Roth} M.~M.,  et~al., 2005, \mn@doi [\pasp] {10.1086/429877}, \href
  {http://adsabs.harvard.edu/abs/2005PASP..117..620R} {117, 620}

\bibitem[\protect\citeauthoryear{{Steidel}, {Erb}, {Shapley}, {Pettini},
  {Reddy}, {Bogosavljevi{\'c}}, {Rudie}  \& {Rakic}}{{Steidel}
  et~al.}{2010}]{2010ApJ...717..289S}
{Steidel} C.~C.,  {Erb} D.~K.,  {Shapley} A.~E.,  {Pettini} M.,  {Reddy} N.,
  {Bogosavljevi{\'c}} M.,  {Rudie} G.~C.,   {Rakic} O.,  2010, \mn@doi [\apj]
  {10.1088/0004-637X/717/1/289}, \href
  {http://adsabs.harvard.edu/abs/2010ApJ...717..289S} {717, 289}

\bibitem[\protect\citeauthoryear{{Swaters}, {Sancisi}, {van Albada}  \& {van
  der Hulst}}{{Swaters} et~al.}{2009}]{2009A&A...493..871S}
{Swaters} R.~A.,  {Sancisi} R.,  {van Albada} T.~S.,   {van der Hulst} J.~M.,
  2009, \mn@doi [\aap] {10.1051/0004-6361:200810516}, \href
  {http://adsabs.harvard.edu/abs/2009A%26A...493..871S} {493, 871}

\bibitem[\protect\citeauthoryear{{Tasitsiomi}}{{Tasitsiomi}}{2006}]{2006ApJ...645..792T}
{Tasitsiomi} A.,  2006, \mn@doi [\apj] {10.1086/504460}, \href
  {http://adsabs.harvard.edu/abs/2006ApJ...645..792T} {645, 792}

\bibitem[\protect\citeauthoryear{{Tassis}, {Kravtsov}  \& {Gnedin}}{{Tassis}
  et~al.}{2008}]{2008ApJ...672..888T}
{Tassis} K.,  {Kravtsov} A.~V.,   {Gnedin} N.~Y.,  2008, \mn@doi [\apj]
  {10.1086/523880}, \href {http://adsabs.harvard.edu/abs/2008ApJ...672..888T}
  {672, 888}

\bibitem[\protect\citeauthoryear{{Thuan} \& {Izotov}}{{Thuan} \&
  {Izotov}}{1997}]{Thuan97}
{Thuan} T.~X.,  {Izotov} Y.~I.,  1997, \apj, \href
  {http://adsabs.harvard.edu/abs/1997ApJ...489..623T} {489, 623}

\bibitem[\protect\citeauthoryear{{Tollerud}, {Bullock}, {Graves}  \&
  {Wolf}}{{Tollerud} et~al.}{2011}]{2011ApJ...726..108T}
{Tollerud} E.~J.,  {Bullock} J.~S.,  {Graves} G.~J.,   {Wolf} J.,  2011,
  \mn@doi [\apj] {10.1088/0004-637X/726/2/108}, \href
  {http://adsabs.harvard.edu/abs/2011ApJ...726..108T} {726, 108}

\bibitem[\protect\citeauthoryear{{Trainor}, {Strom}, {Steidel}  \&
  {Rudie}}{{Trainor} et~al.}{2016}]{Trainor16}
{Trainor} R.~F.,  {Strom} A.~L.,  {Steidel} C.~C.,   {Rudie} G.~C.,  2016,
  \mn@doi [\apj] {10.3847/0004-637X/832/2/171}, \href
  {http://adsabs.harvard.edu/abs/2016ApJ...832..171T} {832, 171}

\bibitem[\protect\citeauthoryear{{Verhamme}, {Schaerer}  \&
  {Maselli}}{{Verhamme} et~al.}{2006}]{2006A&A...460..397V}
{Verhamme} A.,  {Schaerer} D.,   {Maselli} A.,  2006, \mn@doi [\aap]
  {10.1051/0004-6361:20065554}, \href
  {http://adsabs.harvard.edu/abs/2006A%26A...460..397V} {460, 397}

\bibitem[\protect\citeauthoryear{{Verhamme}, {Orlitov{\'a}}, {Schaerer}  \&
  {Hayes}}{{Verhamme} et~al.}{2015}]{2015A&A...578A...7V}
{Verhamme} A.,  {Orlitov{\'a}} I.,  {Schaerer} D.,   {Hayes} M.,  2015, \mn@doi
  [\aap] {10.1051/0004-6361/201423978}, \href
  {http://adsabs.harvard.edu/abs/2015A%26A...578A...7V} {578, A7}

\bibitem[\protect\citeauthoryear{Walt, Colbert  \& Varoquaux}{Walt
  et~al.}{2011}]{numpy}
Walt S. v.~d.,  Colbert S.~C.,   Varoquaux G.,  2011, Computing in Science \&
  Engineering, 13, 22

\bibitem[\protect\citeauthoryear{{Yamada}, {Matsuda}, {Kousai}, {Hayashino},
  {Morimoto}  \& {Umemura}}{{Yamada} et~al.}{2012}]{2012ApJ...751...29Y}
{Yamada} T.,  {Matsuda} Y.,  {Kousai} K.,  {Hayashino} T.,  {Morimoto} N.,
  {Umemura} M.,  2012, \mn@doi [\apj] {10.1088/0004-637X/751/1/29}, \href
  {http://adsabs.harvard.edu/abs/2012ApJ...751...29Y} {751, 29}

\makeatother
\end{thebibliography}

>>>>

The models we use correspond to simplified geometrical configurations.
This allows us to perform a deep exploration of parameter space and
gain some physical insight into \tol's kinematic properties.
In this paper we show, for the first time in the literature, that \tol's
\lya profile can be explicitly modeled by either of these two
models.

@@

Which model could be closer to the actual kinematic conditions in \tol?  
Recent Integral Field Unit (IFU) observation of other CDGs seem to
favor the multiphse model \citep{2015A&A...577A..21C,2017A&A...600A.125C}. 
These observations  were performed with the Visible Multi-Object Spectrograph (VIMOS)
\citep{2003SPIE.4841.1670L}.
The spatial smapling was $0.67$ arcseconds and covered about
$30^{\prime\prime}\times 30^{\prime\prime}$ on the sky. 
They observed nine BCGs to produce two-dimensional maps of the
continuum and promiment emission lines, this allowed them to produce 
two-dimensional velocitity field maps using the H$\alpha$ emission
line.
They find velocity fields ranging from simple rotation patterns 
(with amplitudes of $10-120\kms$) to highly irregular. 
The velocity dispersion in most cases is typically less than $50$ \kms
with the exception of one galaxy that shows a dispersion of $130$
\kms.

The hybrid case of a rotating multiphase configuration is also of
interest, but cannot be simulated with in current models. 
However, it is the subject of ongoing work  (Remolina-Gutierrez et
al. in prep.).

We argue that that the rotation model should be discarded by
considering that the prefered rotational velocity of $V_{m}\sim350$
\kms\ is of the same order as the largest rotational velocity of giant
disc galaxies that have two orders of magnitude more baryonic mass
than \tol\ \citep{2015MNRAS.448.1767C}.

@@

\bibliographystyle{mnras}
\bibliography{references}
